\section{Body - defining Bodies}

An INI file can contain an arbitrary number of sections defining bodies. Each body section is opened by \lstinline{[BODY: NAME]} where \lstinline{BODY:} defines the bodies type and \lstinline{NAME} is an unique name to tell different bodies with equal types apart. The \lstinline{order} and the \lstinline{shift_vector} parameters are supported by all bodies but not mandatory. They will be explained later (???TODO ADD REFERENCE???).

\paragraph{Important:} All vectors inside a body section are specified in lattice coordinates by default. For every vector specified in cartesian coordinates the additional parameter \lstinline{someparameter_coordsys} must be added. Its value is either \lstinline{lattice} or \lstinline{cartesian}.

\subsection{Non-periodic bodies}
\input{sphere}
\input{convex_polyhedron}
\input{cylinder}
\subsection{1D-periodic bodies}
Apart from the periodity section being a mandatory part of the configuration there is no fundamental difference between creating 1D-periodic structures and non-periodic ones. The resulting supercell is rotated around the origin so that the axis vectors defined in periodicity section it parallel to the z-Axis.

\input{periodic_1D_cylinder}
\input{periodic_1D_convex_prism}

\subsection{2D-periodic bodies}

Apart from the periodity section being a mandatory part of the configuration there is no fundamental difference between creating 1D-periodic structures and non-periodic ones. The resulting supercell is rotated around the origin so that the z-Axis is orthogonal to both axis vectors defined in the periodicity section.